Multi-domain, multilingual translation with latent multi-task group dropout

### 2021-11-09 2022/acl/acl_latex-fy.tex
suggestions by fy

\title{Multi-domain, multilingual translation with latent multi-task group dropout}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

@@

\section{Introduction}
Multi-domain translation and multilingual translation develop one model for translations in multi-domain and multiple language pairs, respectively. These paradigms are motivated by the compactness of the translation model \cite{dabre20survey,Chu18multilingual} and the hypothetical positive knowledge transfer between similar domains \citep{Pham21revisiting} or between languages in the same family \citep{Tan19multilingual}. However, sharing parameters of the model can cause the catastrophic interference between unrelated tasks \citep{conneau20unsupervised,wang20negative}.

>>>>

\title{Multi-domain, multilingual translation with latent multi-task group dropout}
\title{Latent group dropout for multilingual and multidomain machine translation}
% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

@@

\begin{abstract}
  [FY] Multi-domain and multi-lingual machine translation often rely on parameter sharing strategies, where large portions of the network are meant to capture the commonalties of the task at hand, while smaller parts are reserved to model the peculariaties of a language or a domain. In adapter-based approaches, these strategies are hard coded in the network architecture. In this work, we propose a new method aimed at learning the parameter sharing pattern, using a latent-variable model. We show how this model can be trained end to end, and report experimental results which show that the learned pattern are both meaningful, and yield improved translation performance without any increase of the model size. 
\end{abstract}

\section{Introduction}
Multi-domain and multilingual machine translation (MMT) aim to develop one single model to perform translations for multiple domains and multiple language pairs, respectively. These paradigms are motivated by the compactness of the resulting translation system \citep{dabre20survey,Chu18multilingual}, the hypothetical positive knowledge transfer between similar domains \citep{Pham21revisiting} or between languages in the same family \citep{Tan19multilingual}. However, having all the tasks use exactly the same model parameters can cause negative interference between unrelated tasks \citep{conneau20unsupervised,wang20negative}. Hence the recent development of approaches relying on a partial sharing of the parameters, eg.\ using the adapter layer of \citet{Bapna19simple,houlsby19parameter,Pham20Study}.
